---
title: "DATA_605_Assign_13_DThonn"
file: DATA_605_Assign_13_DThonn
name: Daniel Thonn
output:
  html_document: default
  pdf_document: default
course: DATA 605 CUNY MSDA program
---

** DATA_605_Assignment 13 - Calculus 1 -Testbuilder **

http://rpubs.com/danthonn/384416

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``````{r, echo=TRUE}
if (!require(Deriv)) install.packages("Deriv")
library(Deriv)

if (!require(stats)) install.packages("stats")
library(stats)

if (!require(rootSolve)) install.packages("rootSolve")
library(rootSolve)

Sys.setenv(JAVA_HOME = "C:/Program Files/Java/jre1.8.0_171")

if (!require(rJava)) install.packages("rJava")
library(rJava)

if (!require(rSymPy)) install.packages("rSymPy")
library(rSymPy)

```



** Question-1 **

1). Provide a scatterplot of LifeExp~TotExp, and run simple linear regression. Do not transform the variables. Provide and interpret the F statistics, R^2, standard error,and p-values only. Discuss whether the assumptions of simple linear regression met.


$$\int 4e^{-7x} \, dx$$


``````{r, echo=TRUE}

x <- Var("x")

sympy("integrate(4 * exp(-7 * x))")

## [1] "-4*exp(-7*x)/7"




```

2). Biologists are treating a pond contaminated with bacteria. The level of contamination is changing at a rate of
dN/dt = -3500/t^4 -??? 220 bacteria per cubic centimeter per day, where t is the number of days since treatment began. Find a function N( t ) to estimate the level of contamination if the level after 1 day was 6530 bacteria per cubic centimeter.


``````{r, echo=TRUE}

# rate of change function
f1 <- function(t) -3150 * t^-4 - 220

# integrate f1 to get int_f1
# int_f1 = 1050 * t^-3 - 220 * t + C

# Find C
# Plug in output
# int_f1 = 6530 = 1050 * t^-3 - 220 * t + C

# Solve for C
t <- 1
(C <- 6530 - 1050 * t^-3 + 220 * t)

#C:
# [1] 5700

# int_f1
(int_f1 <- function(t) 1050 * t^-3 - 220 * t + 5700)

# Answer: Function to estimate the level of contamination
# function(t) 1050 * t^-3 - 220 * t + 5700

```

3). Find the total area of the red rectangles in the figure below, where the 3. equation of the line is f ( x ) = 2x  9.



``````{r, echo=TRUE}

# Create a function to represent the equation of the line
f1 <- function(x)( 2 * x - 9)

# left side = 4.5
left <- 4.5
# [1] 4.5
(right <- left + 4)
# [1] 8.5


# Find the total area
# integrate the function f1 from the left limit to the right limit of the rectangles
stats::integrate(Vectorize(f1), left, right)
## 16 with absolute error < 1.8e-13



```

4). Find the area of the region bounded by the graphs of the given equations.

1). y = x2 - 2x - ,

2). y = x + 2

``````{r, echo=TRUE}

# y1 =x^2 −2x −2 
# y2 =x + 2 

# prepare the two equation functions
f1 <- function(x) x^2 - 2 * x - 2
f2 <- function(x) x + 2

# prepare an input data set to for input to the two functions
data <- seq(-2, 5, by = 0.01)

# run the two functions on the data
f1_data <- f1(data)
f2_data <- f2(data)

# plot the data - notice the two intersection points
plot(data, f1_data, type = "l", col = "blue")
lines(data, f2_data, col = "red", type = "l")
abline(0, 0)

# now, locate the intersections
is_equal <- f2_data == f1_data
df1 <- data.frame(cbind(data, is_equal))
intersection_points <- subset(df1, is_equal == 1)
str(intersection_points)

# roots and key poihnts
roots <- uniroot.all(f1, c(-2, 5))
low1 <- roots[1]
up1 <- roots[2]
low2 <- intersection_points$data[1]
up2 <- intersection_points$data[2]

# Answer-5
(integrate(Vectorize(f2), low2, up2)$value - integrate(Vectorize(f1), 
    low2, up2)$value)
# [1] 20.83333


```


5). A beauty supply store expects to sell 110 flat irons during the next year. It costs $3.75 to store one flat iron for one year.  There is a fixed cost of $8.25 for each order. Find the lot size and the number of orders per year that will minimize inventory costs.

``````{r, echo=TRUE}

# sales_num = 110 / yearly_orders

# cost = sales_quant * 3.75 + yearly_orders * 8.25

total_amount <- function(yearly_orders) 110/yearly_orders * 3.75 + 8.25 * 
    yearly_orders
(total_amount.int <- Deriv(total_amount))

# the function (yearly_orders) 
# 8.25 - 412.5/yearly_orders^2

(root <- uniroot.all(total_amount.int, c(1, 110)))
# [1] 7.071079

# Answers;
yearly_orders <- floor(root)
yearly_orders
# [1] 7

units_per_order <- ceiling(110/yearly_orders)
units_per_order
# [1] 16

total_units_sold <- yearly_orders * units_per_order
total_units_sold
# [1] 112

min_cost <- units_per_order * 3.75 + 8.25 * yearly_orders
min_cost
# [1] 117.75


```


6). Use integration by parts to solve the integral below.

$$\int ln(9x)*x^6  \, dx$$

``````{r, echo=TRUE}


x <- Var("x")

# integrate the equation using sympy
sympy("integrate(log( 9 * x ) * x**6)")

#Answer-6:
# [1] "x**7*log(9)/7 + x**7*log(x)/7 - x**7/49"




```


7). Determine whether f (x) is a probability density function on the interval 1, e6 . If not, determine the value of the
definite integral.

f (x) = 1/6x

``````{r, echo=TRUE}

f1 <- function(x) 1/(6 * x)
low <- 1
up <- exp(6)

all.equal(1, integrate(Vectorize(f1), low, up)$value, tolerance = 10^-6)

# Answer-7: f(x) is probability density function
# [1] TRUE

```




** END **


``````{r, echo=TRUE}

```


